Study Comparison

### 2023-12-18 analysis/study_comaprison.Rmd
minor changes to study comparison

# add ventilation
vent <- left_join(
  air %>% 
    mutate(date = as.Date(date),
           class = ifelse(class == "A/B", "A", ifelse(class == "D", "B", class))) %>%
    group_by(year_num, class, week, date) %>%
    slice(1) %>%
    ungroup() %>%
    dplyr::select(year_num, class, week, date),
  odf %>%
    group_by(school, classroom, date) %>%
    slice(1) %>%
    ungroup() %>%
    mutate(year_num = lubridate::year(date),
           class = ifelse(classroom == "AB", "A",
                          ifelse(year_num == 2022 & school == "School 2" & classroom == "A", "B", classroom))) %>%
    dplyr::select(year_num, class, date, co2.max) 
) %>%
  group_by(year_num, class, week) %>%
  summarize(co2.max = mean(co2.max, na.rm = T)) %>%
  ungroup() %>%
  group_by(year_num) %>%
  mutate(co2.max = ifelse(is.na(co2.max), mean(co2.max, na.rm = T), co2.max)) %>%
  ungroup() %>%
  rename(maxCO2 = co2.max)

@@

@@

```{r}
# add prior scales
stanDF$s_saliva <- 1 / sd(stanDF$saliva)
stanDF$s_cov <- 1 / sd(stanDF$cov)
stanDF$s_masks <- .25 #/ sd(stanDF$masks)
stanDF$s_air <- .25 #/ sd(stanDF$air_cleaners)
stanDF$s_co2 <- .25
stanDF$s_cov <- 1

@@

```{r}
# adjusted OR of mask wearing
mod %>%
  spread_draws(beta_cov) %>%
  mutate(beta_cov = exp(beta_cov)) %>%
  median_qi()

>>>>

# add ventilation
vent <- left_join(
  air %>% 
    mutate(date = as.Date(date),
           class = ifelse(class == "A/B", "A", ifelse(class == "D", "B", class))) %>%
    group_by(year_num, class, week, date) %>%
    slice(1) %>%
    ungroup() %>%
    dplyr::select(year_num, class, week, date),
  odf %>%
    group_by(school, classroom, date) %>%
    slice(1) %>%
    ungroup() %>%
    mutate(year_num = lubridate::year(date),
           class = ifelse(classroom == "AB", "A",
                          ifelse(year_num == 2022 & school == "School 2" & classroom == "A", "B", classroom))) %>%
    dplyr::select(year_num, class, date, co2.max) 
) %>%
  group_by(year_num, class, week) %>%
  summarize(maxCO2_imputed = ifelse(is.na(co2.max), T, F), 
            co2.max = mean(co2.max, na.rm = T)) %>%
  ungroup() %>%
  group_by(year_num) %>%
  mutate(co2.max = ifelse(is.na(co2.max), mean(co2.max, na.rm = T), co2.max)) %>%
  ungroup() %>%
  rename(maxCO2 = co2.max)

@@

pair_df %>%
  group_by(year_num, class, week) %>%
  slice(1) %>%
  ungroup() %>%
  filter(!maxCO2_imputed) %>%
  group_by(year_num) %>%
  summarize(mean(maxCO2), sd(maxCO2)) %>%
  mutate_if(is.numeric, round, 0)

@@

```{r}
# add prior scales
stanDF$s_saliva <- sd(stanDF$bioaerosol) / sd(stanDF$saliva)
stanDF$s_cov <- sd(stanDF$bioaerosol) / sd(stanDF$cov)
stanDF$s_masks <- .5 * sd(stanDF$bioaerosol) / sd(stanDF$masks)
stanDF$s_air <- .5 * sd(stanDF$bioaerosol) / sd(stanDF$air_cleaners)
stanDF$s_co2 <- sd(stanDF$bioaerosol)

@@

```{r}
# adjusted OR of mask wearing
mod %>%
  spread_draws(beta_cov) %>%
  mutate(beta_cov = exp(beta_cov)) %>%
  median_qi() %>%
  mutate_if(is.numeric, round, 1)
